TBD

### 2016-10-19 paper.tex
improving first sections

\subsection{Indexing Functions}
In general there are two ways of indexing the visibilities associated with different baselines. We can use the composite index $pq$, which is the strategy that is followed in Eq.~\eqref{eq:vis_definition},
or we can use a single unique baseline index which we assign in numerical order to each composite index; assuming the composite indexes are placed in standard baseline ordering.
The composite indexes $pq$ are ordered using standard baseline ordering

If an array is redundant then its redundant baselines sample the exact same visibilites in the $uv$-plane, i.e. if baseline $pq$ and $rs$ are redundant then $y_{pq} = y_{rs}$. We can
therefore also use the following useful indexing strategy: we can use singular redundant baseline indexes instead of composite antenna pairs to label the true observed visibilities.

Let $\phi_{ij}:\mathbb{N}^2\rightarrow\mathbb{N}^+$ be the function that maps composite antenna pairs to the unique redundant baseline indexes of an array. We refer to this function 
as the redundant array geometry function in this paper. This mapping is not symmetric as 
$\phi_{ij} = 0$ if $i>j$. We can also define the following symmetric variant of $\phi_{ij}$:
\begin{equation}
\zeta_{ij} = 
\begin{cases}
\phi_{ij}~\textrm{if}~i\leq j\\
\phi_{ji}~\textrm{if}~i>j
\end{cases}.
\end{equation} 
It is possible to construct a simple analytic expression for $\zeta_{ij}$ when our array is in an east-west regular configuration, namely $\zeta_{ij} = |j-i|$. 
It becomes increasingly more difficult to construct analytic expressions of $\zeta_{ij}$ for other more complicated array layouts. The empirically constructed symmetric geometry
functions of three different redundant layouts are depicted in Fig.~\ref{fig:geometry_function}. We denote the range of $\zeta_{ij}$ with $\mathcal{R}(\zeta_{ij})$. The maximal element 
that $\zeta_{ij}$ can ascertain is denoted by $L$ and can be construed as the maximal number of unique redundant baselines which can be formed for a given 
array layout. Alternatively, we can interpret the symmetric geometry functions 
in Fig.~\ref{fig:geometry_function} as matrices. In this alternative paradigm, $\zeta_{ij}$ denotes a matrix entry instead. The dimension of these so called geometry 
matrices are $N\times N$, where $N$ denotes the number of antennas in the array.

>>>>

\subsection{Indexing Functions}
In general there are two ways of indexing the true visibilities associated with different baselines. We can use the composite index $pq$, which is the strategy that is followed in Eq.~\eqref{eq:vis_definition},
or we can use a single unique baseline index which we assign in numerical order to each composite index; assuming the composite indexes are arranged in standard baseline order.
The composite indexes $pq$ are in standard baseline order when they are arranged as follow: $12, 13, 1N, 23\cdots$. We use $N$ to denote the number of antennas in the array. Let 
\begin{equation}
\alpha_{pq} =
\begin{cases}
(q-p) + (p-1)\left (N-\frac{1}{2}p \right ) & \textrm{if}~p<q\\
%B + (p-q) + (q-1)\left (N-\frac{1}{2}q \right )) & \textrm{if}~p>q\\
%B+q + \frac{1}{2}(p-1)(p-2) & \textrm{if}~p>q\\
0 & \textrm{otherwise}
\end{cases}.
\end{equation}
We can use $\alpha_{pq}$ to map composite indexes to unique baseline indexes, i.e. 
\begin{equation}
12,13,\cdots,1N,23,\cdots \xrightarrow{\alpha_{pq}} 1,2,3,\cdots,B.
\end{equation}
Moreover, $B$ denotes the number of baselines in the array, i.e. $B = \frac{N^2-N}{2}$.

If an array is redundant then its redundant baselines should sample the exact same visibilities in the $uv$-plane, i.e. if baseline $pq$ and $rs$ are redundant then $y_{pq} = y_{rs}$. The 
fact that redundant baselines should measure the exact same visibility implies that every baseline does not require a unique baselines index; instead we can use a separate index for each unique redundant baseline. Let $\phi_{pq}$ be the function that maps composite antenna pairs to the redundant baseline indexes of an array. Note that $\phi_{pq}$ is not symmetric as 
$\phi_{pq} = 0$ if $p>q$. We can also define the following symmetric variant of $\phi_{pq}$:
\begin{equation}
\zeta_{ij} = 
\begin{cases}
\phi_{pq}~\textrm{if}~p \leq q\\
\phi_{qp}~\textrm{if}~p>q
\end{cases}.
\end{equation} 
It is possible to construct a simple analytic expression for $\zeta_{pq}$ when our array is in an east-west regular configuration, namely $\zeta_{pq} = |q-p|$. 
It becomes increasingly more difficult to construct analytic expressions of $\zeta_{pq}$ for other more complicated array layouts. The empirically constructed symmetric geometry
functions of three different redundant layouts are depicted in Fig.~\ref{fig:geometry_function}. We denote the range of $\zeta_{ij}$ with $\mathcal{R}(\zeta_{ij})$. The maximal element 
that $\zeta_{ij}$ can ascertain is denoted by $L$ and can be construed as the maximal number of unique redundant baselines which can be formed for a given 
array layout. Alternatively, we can interpret the symmetric geometry functions 
in Fig.~\ref{fig:geometry_function} as matrices. In this alternative paradigm, $\zeta_{ij}$ denotes a matrix entry instead. The dimension of these so called geometry 
matrices are $N\times N$, where $N$ denotes the number of antennas in the array.
